Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
change the introduction and the code of graph 2

ggplot(theft_data_melted, aes(x = Year, y = TheftRate)) +
  geom_boxplot(aes(fill = Year)) +
  labs(title = "Box plot of theft rates by year (2014-2023)",
       x = "Year",
       y = "Theft rate (per 100,000 people)") +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

# Assuming crime_rates_data is already loaded
theft_data <- crime_rates_data %>% 
  select(starts_with("THEFTOVER_RATE"), AREA_NAME) %>%
  pivot_longer(cols = -AREA_NAME, names_to = "Year", values_to = "TheftRate", 
               names_prefix = "THEFTOVER_RATE_")

# Generate the box plot with ggplot2
ggplot(theft_data, aes(x = Year, y = TheftRate, fill = Year)) +
  geom_boxplot() +
  labs(title = "Box plot of theft rates by year (2014-2023)",
       x = "Year",
       y = "Theft rate (Per 100,000 people)") +
  theme_minimal() +
  theme(legend.position = "none")
```
